landlord

### 2022-10-22 src/landlord.Rmd
landlord scores calculated

#input landlord weights for each indicator in the following order: rent control, security deposit limit, notice for entry, eviction notice days
#Get weights from Owen
#Weights must sum to 1
landlord_weights <- c(0.5, 0.1, 0.1, 0.3)
size <- dim(MSA_landlord_data)
for (x in 1:size[1]) {
  print(x)
}
x```

>>>>

#input landlord weights for each indicator in the following order: rent control, security deposit limit, notice for entry, eviction notice days
#Get weights from Owen
#Weights must sum to 1
landlord_weights <- c(0.25, 0.25, 0.25, 0.25)

#make landlord_score column
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    landlord_score = MSA #this is just a place holder
  )
size <- dim(MSA_landlord_data)
for (i in 1:size[1]) {
  MSA_x_data <- c(MSA_landlord_data$rent_control_binary[i], 
                  MSA_landlord_data$security_depopsit_limit_binary[i],
                  MSA_landlord_data$notice_for_entry_days_binary[i],
                  MSA_landlord_data$eviction_notice_days_normalized_inverted[i])
  MSA_landlord_data$landlord_score[i] = weighted.mean(MSA_x_data, landlord_weights)
}
```
